\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-05-26 AffineLieAlgebras/InformalNotes/article.tex
Some work on physics section

Consider the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors at the Figure \ref{fig:B2_A1}. We denote the corresponding Weyl reflections by $\omega_1, \omega_2$. Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$ and is drawn as grey vector.

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$, which is drawn as the black vector at the Figure \ref{fig:B2_A1}.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

Substituting the branching rules into \eqref{eq:34} we get non-diagonal mass matrix
\begin{equation}
  \label{eq:2}
  M_{\lambda\xi,\mu\eta}
\end{equation}
where $\lambda,\mu$ are the highest weights of the representations of $\mathfrak{a}_1$ and $\xi,\eta$ of $\mathfrak{a}_2$. A new $\mathfrak{a}_1$-invariant mass matrix can be found by the contraction of $M_{\lambda\xi,\mu\eta}$ with some known $\mathfrak{a}_2$-invariant mass matrix $M^{(2)}_{\xi\eta}$:
\begin{equation}
  \label{eq:35}
  M^{(1)}_{\lambda\mu}=\sum_{\xi,\eta\in P_{\mathfrak{a}}^{+}}M_{\lambda\xi,\mu\eta}M^{(2)}_{\xi\eta}
\end{equation}

>>>>

Consider the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors at the Figure \ref{fig:B2_A1}. We denote the corresponding Weyl reflections by $\omega_1, \omega_2$. Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+2\alpha_2$ and is drawn as grey vector.

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$, which is drawn as the black vector at the Figure \ref{fig:B2_A1}.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho)-\rho,\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

Substituting the branching rules into \eqref{eq:34} we get non-diagonal mass matrix
\begin{equation}
  \label{eq:2}
  M_{\lambda\xi,\mu\eta}
\end{equation}
where $\lambda,\mu$ are the highest weights of the representations of $\mathfrak{a}_1$ and $\xi,\eta$ of $\mathfrak{a}_2$.
